Empty Homes V1

### 2017-06-26 LowUseEngland.Rmd
Code streamline
Ugraded the bootsrapping function so it does both value and class strapping at the same time. 
made a new function that does a value ttest and outputs a bunch of useful stats about the difference between homes and low-use homes.

 z1<-   ls(pattern = "CUMBRIA") %>% map_df(~eval(parse(text=.x)))   %>% BootStrapTtest(.)

@@

@@

read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
  StructureData(lowuse = c(2,7:16, 21:28) ) %>%
  PlotMap(., AG,title = "all empties")

@@

 z1<-   ls(pattern = "Cornwall") %>% map_df(~eval(parse(text=.x)))   %>% BootStrapTtest(.)

CornStrap<- ls(pattern = "Cornwall") %>% map_df(~eval(parse(text=.x))) %>%
   DistribCompareBootstrapper(., 1652, 1000)

@@

@@

 z1<-   ls(pattern = "CoastWave") %>% map_df(~eval(parse(text=.x)))   %>% BootStrapTtest(.)

@@

>>>>

@@

Cumbriattest <- ValueTtest(CumbriaStrap)

@@

# read_excel("Cornwall.xlsx", sheet=1)%>% setNames(make.names(names(.))) %>% .[,1:4] %>%
#   StructureData(lowuse = c(2,7:16, 21:28) ) %>%
#   PlotMap(., AG,title = "all empties")

@@

Cornstrap <-DistribCompareBootstrapper(Cornwall, 1652, 100)

@@

Cornttest <- ValueTtest(Cornstrap)

Cornttest$data.frame %>% select(LowUsePrice,HomesPrice) %>%
  gather(key ="type", "meanprice") %>%
  ggplot(., aes(x= type, y = meanprice, fill = type)) + geom_boxplot()

@@

@@

Suffttest <- ValueTtest(SuffStrap)

### 2017-06-26 LowUseLondon.Rmd
Code streamline
Ugraded the bootsrapping function so it does both value and class strapping at the same time. 
made a new function that does a value ttest and outputs a bunch of useful stats about the difference between homes and low-use homes.

#Chelsea sums
```{r}

@@

#the data is not normal
plot(density(v))
#this prob not valid
t.test(v,alternative = "greater")

#do a bootstrapped mean to see if it is greater than the mean of the homes overall.
set.seed(1258)
samps <-10000

bootres <- 1:samps %>% map(~data.frame(res =sample(v, length(v), replace = T))) %>%
  bind_cols()

sum(colMeans(bootres)>0)/samps

Chelseainfo %>% filter(LAD11CD =="E09000020") %>%
  BootStrapTtest(.)

plot(density(colMeans(bootres+ChelMeanPrice)))

prices %>% filter(X14== "GREATER LONDON") %>% summarise(mean = mean(X2))
Admin_ward_code
#c("Lower Mainstream", "Mid Mainstream", "Upper Mainstream", "Prime", "Super Prime"),
ClassCountsPerWard <- prices %>% 
  filter( Admin_district_code =="E09000020") %>%
  mutate(class = cut(X2, c(0,  490,      750,   2000, 12000, Inf)*10^3, 
            labels =     c("Lower", "Mid", "Upper", "Prime", "Super"), 
             right = F)) %>%
  select(Admin_ward_code, class) %>%
  group_by(Admin_ward_code, class) %>% 
  summarise(Counts = n()) %>%
  group_by(Admin_ward_code) %>%
  mutate(WardPerc = Counts/sum(Counts)) %>%
  ungroup

test3 <- Chelseainfo %>% 
  group_by(Admin_ward_code) %>%
  summarise_all(funs(first)) %>%
  select(Admin_ward_code, WardLowUse, WardHomes) %>%
  left_join(., ClassCountsPerWard, "Admin_ward_code") %>%
  mutate(LowUseClass = WardLowUse*WardPerc,
         HomesClass = WardHomes*WardPerc) %>%
  group_by(class) %>%
  summarise(LowUseClass = sum(LowUseClass),
            HomesClass = sum(HomesClass)) %>%
  filter(complete.cases(.)) %>%
  mutate(PercOfLowUse = LowUseClass/sum(LowUseClass),
         PercOfHomes = HomesClass/sum(HomesClass),
         PercofClass = LowUseClass/HomesClass,
         `Expected Homes` = PercOfHomes*sum(LowUseClass),
         `Actual Homes` = LowUseClass)

sum(test3$LowUseClass)*test3$PercOfHomes

#Percentage over and under of what would be expected if buying was random
#The differences suggest that people are buying more expensive homes when there is no plan to live in them.
round(test3$LowUseClass/(sum(test3$LowUseClass)*test3$PercOfHomes),2)

ggplot(test3, aes(x= class, y = PercOfHomes*100)) +geom_bar(stat = "identity") + 
  labs(title = "Distribution probability of homes in each class", y = "Percentage")

test3 %>%
  select(class, `Expected Homes`, `Actual Homes`) %>%
  gather(key = "Type" , value = "Number", -class) %>%
  ggplot(., aes(x= class, y = Number, fill = Type)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Expected Number of low-use homes in each class")

test3 %>%
  mutate(`Percentage Difference` = (`Actual Homes`/`Expected Homes`)*100-100) %>%
  ggplot(., aes(x= class, y = `Percentage Difference`)) +
  geom_bar(stat = "identity") +
  labs(title = "Percentage difference between expected number of homes per class and actual")+
  coord_cartesian(ylim=c(-20,20))

#Chelsea Bootstrapped ratios

```{r}

chelstrap <-  Chelseainfo %>% filter(LAD11CD=="E09000020") %>% 
  DistribCompareBootstrapper(., 1652, 100)

@@

test1 %>% group_by(class) %>%
  summarise_all(funs(mean))

>>>>

#Chelsea Bootstrapped ratios
```{r}

@@

chelstrap <-  Chelseainfo %>% filter(LAD11CD=="E09000020") %>% 
  DistribCompareBootstrapper(., 1652, 1000)

@@

 Chelttest <- ValueTtest(chelstrap)
